Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-11 method.tex
Clarified order of magnitude statements in section 2.2
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1025 ccdd05d5-56c1-461a-bf98-85f6876523b4

The first transformation is to chop the \TD{} templates up into \emph{time
slices}.  Since each template slice is disjoint in time, the resulting set for
a single template is orthogonal.  Given the chirp-like structure of the
templates, the early time slices have significantly lower bandwidth and can be
safely downsampled.  The downsampling reduces the number of data samples by a
factor of $\sim$100 from the early part of the waveform and allows the filters
to be evaluated at about $\sim$$1/100^\mathrm{th}$ the sample rate. Since the
computational cost of \TD\ filtering is quadratic in the filter length, this
amounts to more than a factor of $10^4$ reduction in the floating-point operations
 per second required to filter the early part of the waveform.

>>>>

The first transformation is to chop the \TD{} templates up into \emph{time
slices}.  Since each template slice is disjoint in time, the resulting set for
a single template is orthogonal.  Given the chirp-like structure of the
templates, the early time slices have significantly lower bandwidth and can be
safely downsampled.  Downsampling reduces the total number of filter coefficients
by a factor of $\sim$100 by treating the earliest part of the waveform
at $\sim$$1/100$ of the full sample rate. Since the
computational cost of \TD\ filtering is quadratic in the filter length, this
amounts to more than a factor of $10^4$ reduction in the floating-point operations
 per second required to filter the early part of the waveform.
